The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
reflow
social threshold results

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased rapidly
between 5 m and 50 m thresholds, followed by a plateau, while graph strength for
summer networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). Layer similarity (Figure \@ref(fig:socres)c) and connective
redundancy (Figure \@ref(fig:socres)d) were relatively stable across social
thresholds. Taken together, these results suggest the optimal 
<!-- TODO: why optimal --> 
social scale at which groups should be assigned is likely somewhere
between ~20 - 100 m based on the rate at which network metrics stabilized. For
ungulates, groups are often assigned based on 50 m threshold (Lingle 2003;
Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
quantities of data, ~50 m is likely an appropriate social scale for generating
social networks in caribou and similar species.
<!-- TODO: missing summer relevance .. the actual value of layer sim?-->

>>>>

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, mean graph strength for summer networks did not
change as the social threshold increased, but graph strength in winter networks
increased rapidly between 5 m and 50 m thresholds, followed by a plateau (Figure
\@ref(fig:socres)a). Layer relevance was stable around 0 during the summer but
increased for winter networks between 5 and 50 m social thresholds, then did not
change for any habitat types (Figure \@ref(fig:socres)b). This pattern suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks. Layer similarity was
not very strong for any habitat type, indicating that summer and winter networks
are only weakly correlated. Furthermore, layer similarity in open habitats
showed more variation as social threshold increased compared to forage and
forest habitats (Figure \@ref(fig:socres)c). Connective redundancy was
relatively stable across social thresholds, especially after 50 m (Figure
\@ref(fig:socres)d). Taken together, these results suggest the optimal social
scale at which groups should be assigned is likely somewhere between ~20 - 100 m
based on the rate at which network metrics stabilized. For ungulates, groups are
often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
is likely an appropriate social scale for generating social networks in caribou
and similar species.
